Appendix

### 2021-05-11 paper/preprint/paper_revised_submission_april2021_apa.Rmd

## Access to social information across age

```{r}
## summary for all detections
face_hand_by_age <- all_vid_data %>%
  ungroup() %>%
  tidyr::replace_na(list(faces_and_hands=0)) %>%
  group_by(age_day_bin, child_id) %>%
  summarize(num_frames_total = sum(num_frames), 
            # prop faces overall
            num_faces = sum(num_faces), 
            num_hands = sum(num_hands), 
            prop_faces = num_faces / num_frames_total, 
            prop_hands = num_hands / num_frames_total,
            # in center FOV
            num_faces_center = sum(num_faces_center, na.rm=TRUE), 
            num_hands_center = sum(num_hands_center, na.rm=TRUE), 
            prop_faces_center = num_faces_center / num_frames_total, 
            prop_hands_center = num_hands_center / num_frames_total,
            # detailed face info
            prop_full_faces = sum(num_full_faces, na.rm=TRUE)/num_frames_total,
            prop_faces_and_hands = sum(faces_and_hands)/num_frames_total,
            # face/hand contingency
            prop_joint_given_faces = sum(faces_and_hands, na.rm=TRUE)/num_faces, 
            prop_joint_given_hands = sum(faces_and_hands, na.rm=TRUE)/num_hands,
            prop_joint_given_faces_center = sum(face_and_hands_center, na.rm=TRUE)/num_faces_center, 
            prop_joint_given_hands_center = sum(face_and_hands_center, na.rm=TRUE)/num_hands_center)

@@

## Fine-grained changes in the social information in view
```{r}
## construct age bins for plotting
bin_size=7
min_age = min(all_vid_bbs$age_days, na.rm=TRUE)
max_age = max(all_vid_bbs$age_days, na.rm=TRUE)
bin_starts = seq(min_age-1, max_age+1,bin_size)
bins = c(bin_starts, max_age)

>>>>

## Access to social information across age
```{r}
## summary for all detections
face_hand_by_age <- all_vid_data %>%
  ungroup() %>%
  tidyr::replace_na(list(faces_and_hands=0)) %>%
  group_by(age_day_bin, child_id) %>%
  summarize(num_frames_total = sum(num_frames), 
            # prop faces overall
            num_faces = sum(num_faces), 
            num_hands = sum(num_hands), 
            prop_faces = num_faces / num_frames_total, 
            prop_hands = num_hands / num_frames_total,
            # in center FOV
            num_faces_center = sum(num_faces_center, na.rm=TRUE), 
            num_hands_center = sum(num_hands_center, na.rm=TRUE), 
            prop_faces_center = num_faces_center / num_frames_total, 
            prop_hands_center = num_hands_center / num_frames_total,
            # detailed face info
            prop_full_faces = sum(num_full_faces, na.rm=TRUE)/num_frames_total,
            prop_faces_and_hands = sum(faces_and_hands)/num_frames_total,
            # face/hand contingency
            prop_joint_given_faces = sum(faces_and_hands, na.rm=TRUE)/num_faces, 
            prop_joint_given_hands = sum(faces_and_hands, na.rm=TRUE)/num_hands,
            prop_joint_given_faces_center = sum(face_and_hands_center, na.rm=TRUE)/num_faces_center, 
            prop_joint_given_hands_center = sum(face_and_hands_center, na.rm=TRUE)/num_hands_center)

@@

## Fine-grained changes in the social information in view

```{r}
## construct age bins for plotting
bin_size=7
min_age = min(all_vid_bbs$age_days, na.rm=TRUE)
max_age = max(all_vid_bbs$age_days, na.rm=TRUE)
bin_starts = seq(min_age-1, max_age+1,bin_size)
bins = c(bin_starts, max_age)
